Inferring Continuous and Discrete Population Genetic Structure Across Space

### 2017-09-15 writeup/conStruct.tex
ultimate tweaks

\paragraph{Implications for management and conservation}
Since isolation by distance is common, 
a likely result of applying \texttt{conStruct} to existing data is that some
populations previously identified using nonspatial clustering methods 
may be collapsed into each other.  
This ``lumping'' might better reflect biological reality, 
but may also have implications for management decisions and conservation policy, 
both of which are often predicated on the identification of discrete ``management units'' (MUs) 
identified using genetic data \cite{Moritz1994,Waples_1998,Moritz_etal_2002}.

@@

\section*{Models, parameters, and priors}\label{model_app}
\paragraph{Spatial versus nonspatial}
In this paper, we discuss two types of models, spatial and nonspatial, 
each of which can be implemented with different numbers of layers/clusters.
The spatial model is parameterized as in Eq.\ \eqref{admixed_spatial_cov},
and the nonspatial model
is a special case of the spatial model with all $\alpha$ parameters is set to 0.
% is described in Eq.\ \eqref{admixed_discrete_covariance}.  % that's not the right eq'n
The nonspatial model therefore has $3K$ fewer parameters than the spatial model,
since three $\alpha$ parameters that describe the continuous differentiation effect of distance in each layer.

>>>>

\paragraph{Implications for management and conservation}
Because isolation by distance is common, 
a likely result of applying \texttt{conStruct} to existing data is that some
populations previously identified using nonspatial clustering methods 
may be collapsed into each other.  
This ``lumping'' might better reflect biological reality, 
but may also have implications for management decisions and conservation policy, 
both of which are often predicated on the identification of discrete ``management units'' (MUs) 
identified using genetic data \cite{Moritz1994,Waples_1998,Moritz_etal_2002}.

@@

\section*{Models, parameters, and priors}\label{model_app}
\paragraph{Spatial versus nonspatial}
In this paper, we discuss two types of models, spatial and nonspatial, 
each of which can be implemented with different numbers of layers/clusters.
The spatial model is parameterized as in Eq.\ \eqref{admixed_spatial_cov},
and the nonspatial model
is a special case of the spatial model with all $\alpha$ parameters is set to 0.
% is described in Eq.\ \eqref{admixed_discrete_covariance}.  % that's not the right eq'n
The nonspatial model therefore has $3K$ fewer parameters than the spatial model,
because there are three $\alpha$ parameters that describe the continuous differentiation effect of distance in each layer.
